Structural replication of nanoporous media using procedural noise

### 2018-05-30 ms.tex
Fixed better conclusion

\section{Conclusion}
\todo{konklusjon maa renskrives}

In this paper, we have proposed a novel method for generating a nanoporous media
using procedural methods in the form of simplex noise.
Procedural methods are not physical, but rather statistical models, and this gives
them some advatages over prevalent methods: they are computationally efficient, have low memory footprints and are only limited in terms of detail by the model in question. 
In particular, it is possible to create simulations of arbitrary scales and resolution, indeed with any level of detail.

\todo{AMS: This is a bit weak currently. State first what you have succeeded in doing.
Then state the possible weaknesses of the model.}
We have developed a framework to generate nanoporous media using molecular dynamics simulations and
to estimate model parameters given such data. 
We have shown that it is possible through a full likelihood analysis to successfully reproduce the
input parameters of procedurally simulated data. 
In addition, we performed an analysis on a simulated $\SI{159}{\angstrom^{3}}$ data set of SiO$_2$,
and explain that while porosity and surface area correspond well between the model and data,
analysis of $g(r)$ shows that the current model reproduces the main features of the material, but that there are some deviations. 
We find the correspondence strong, which demonstrates the proof-of-principle of the use of
procedural noise methods, but we realize that even better correspondence may be achieved by
including other summations in the procedural noise modes.

\subsection{Future work}
We have only considered the simplest kind of procedural noise: a simple sum over modes with
threshold cut-off $\tau$, scale fall-off persistence $\psi$ and initial scale $\nu$. 
We have also seen that, even through both porosity and surface area accurately reproduced,
there are features in the RDF that are not fully captured with the current model. 
This is evident from the images of the simulated structure seen in figure \ref{fig:porous_vs_model},
where the connecting nearly one-atom thin walls are difficult to reproduce with the current model. 
However, as procedural noise exert properties closely related to that of fractals, it is possible
to extend the number of parameters and define new models with very different properties. 
Some examples of these models are depicted in figure \ref{fig:future_models}, where the left- and
centre images show a new model with two new parameters (offset and gain), while the rightmost panel shows a simulation where the scale $\nu$ is itself being perturbed by procedural noise, yielding strong circular asymmetric patterns.

>>>>

\section{Conclusion}
In this paper, we have proposed a novel method for generating porous materials using procedural methods in the form of simplex noise.
Procedural methods are not physical, but rather statistical models, which gives them some advantages over prevalent methods: they are computationally efficient, have low memory footprints and are only limited in terms of detail by the model in question. 
In particular, it is possible to create simulations of arbitrary scales and resolution, indeed with any level of detail.

We have generated a series of statistically similar nanoporous materials with 75 \% porosity using molecular dynamics simulations and a heat, expand and quench method explained above.
These systems have complicated pore networks, and are used as data input to our procedural noise model.
The procedural noise model we have used is similar to what can be found in \cite{groeneboom:2014}, and has degrees of freedom on both short and long length scales.

A full MCMC framework was developed. It takes files with atomic positions as input, deletes atoms according to equation \eqref{eq:delete_threshold} and compares each realization with the input data using different model measures, such as $g(r)$, surface area or porosity.
In our work, we used $g(r)$ to compare a proposed parameter set to the input data.
Our framework is validated by reproducing known parameters on a mock data set with our MCMC code before we run the code on the simulated system from molecular dynamics.
The model reproduces the main features of $g(r)$, but both surface area and porosity were also found to be in good agreement between our best fit model and the data even though they were not used during the fitting process.

However, by visually comparing the two systems in figure \ref{fig:porous_vs_model}, we see clear differences. For instance, covalent bonds are certainly broken, but this is expected since our model just removes atoms with no chemical care.
In addition, the calculated $g(r)$ of our best fit model is lacking some features that exists in the simulated data, such as two weak bumps and a slight lower-valued tail.

We find the correspondence strong, which demonstrates the proof-of-principle of the use of
procedural noise methods, but we realize that even better correspondence may be achieved by including other summations in the procedural noise modes.

\subsection{Future work}
We have only considered the simplest kind of procedural noise: a simple sum over modes with
threshold cut-off $\tau$, scale fall-off persistence $\psi$ and initial scale $\nu$. 
We have also seen that, even though both porosity and surface area accurately reproduced,
there are features in the radial distribution function that are not fully captured with the current model. 
This is evident from the images of the simulated structure seen in figure \ref{fig:porous_vs_model},
where the connecting nearly one-atom thin walls are difficult to reproduce with the current model. 
However, as procedural noise exert properties closely related to that of fractals, it is possible
to extend the number of parameters and define new models with very different properties. 
Some examples of these models are depicted in figure \ref{fig:future_models}, where the left- and
centre images show a new model with two new parameters (offset and gain), while the rightmost panel shows a simulation where the scale $\nu$ is itself being perturbed by procedural noise, yielding strong circular asymmetric patterns.
